### 2012-10-02 docs/runtime_parameters/runtime_parameters.tex
update

\verb=  ppm_type  = &   0 = no ppm \newline 1 = 1985 ppm \newline 2 = Hybrid Sekora/Colella McCorquodale Colella 2009/2010 ppm  &  1 \\

@@

\verb=  slope_order  = &   order of slopes in Godunov algorithm.  Options are 0, 2, or 4.  &  4 \\

>>>>

\verb=  ppm_type  = &   0 = no ppm (piecewise linear slopes instead) \newline 1 = 1984 ppm \newline 2 = Hybrid Sekora/Colella and McCorquodale/Colella 2009/2010 ppm  &  1 \\

@@

\verb=  slope_order  = &   order of slopes in piecewise linear Godunov algorithm.  Options are 0, 2, or 4.  &  4 \\
